Matching the Time of Emergence of Transboundary Fish Stocks to Lead Time for

### 2021-11-24 Scripts/Initial_Analysis.Rmd
Updated repository for data availabillity

toe_data <- bind_rows(lapply(Paths, fread)) %>% 
  filter(
    n_ens == 10
  ) %>% 
  left_join(Exploited_spp_list) %>% 
            select(taxon_key,taxon_name,common_name,everything(),-genus,-species)

write_csv(toe_data, "./Data/toe_data.csv")

@@

>>>>

# toe_data <- bind_rows(lapply(Paths, fread)) %>% 
#   filter(
#     n_ens == 10
#   ) %>% 
#   left_join(Exploited_spp_list) %>% 
#             select(taxon_key,taxon_name,common_name,everything(),-genus,-species)
# 
# write_csv(toe_data, "./Data/toe_data.csv")

@@

### Centroid Supplemental Figure
```{r}
